\begin{abstract}
Topology creation and maintenance protocols are one of the first choices a
designer of a Peer-to-Peer system has to face.
Distributed hash tables (DHTs), such as Chord or Kademlia, are frequently chosen
due to their good performance.
These core protocols rely, however, on correct behavior of their participants
and are thus prone to malicious behavior.
A completely unprotected system may be controlled or shutdown by an adversary
with modest resources.

There exists a rich set of proposals which aim to secure DHTs, and yet most of
the popular and widely used Peer-to-Peer applications using DHTs, such as:
BitTorrent Mainline DHT, Kad, OpenDHT, are not using them and are known to be
insecure. We suspect the reason is that security extensions are found to be
impractical by developers.
Impracticalities include things such as: suboptimal performance, too stringent
assumptions, and lack of robust implementation.

This goal of this work is to design and implement an extensible DHT system
that is protected against a wide array of attacks.
This implementation is done using Java using tested software engineering
practices that provide elasticity and customizability necessary to allow easy
inclusion of the library into an application.

We experimentally verified that the additional time needed by our protocol for
joining the DHT is in the order of 1--4 seconds for up to 21 registration nodes.
A time in the order of seconds means that the new join operation is practical.
\end{abstract}
