\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem[Urd11]{urd11} Guido Urdaneta, Guillaume Pierre, Maarten Van Steen
\textit{A Survey of DHT Security Technologies}, ACM Comput. Surv.  43, 2,
Article 8 (January 2011)

\bibitem[Dou02]{dou02} Doucer, \textit{Proceedings of the 1st International
Workshop on Peer-to-Peer Systems}, Lecture Notes on Computer Science, vol. 2429.
Springer-Verlag, Berlin, Germany, 251–260

\bibitem[Cas02]{cas02} Castro, Druschel, Ganesh, Rowstron, Wallach,
\textit{Secure routing for structured peer-to-peer overlay networks},
ACM SIGOPS Operating Systems Review - OSDI '02: Proceedings of the 5th symposium
on Operating systems design and implementation,
Vol. 36 Issue SI, Winter 2002,
299-314

\bibitem[Hai06]{hai06} 
Haifeng Yu, Michael Kaminsky, Phillip B. Gibbons, Abraham Flaxman,
\textit{Sybilguard: Defending against sybil attacks via social networks},
ACM SIGCOMM ’06, p. 267--278

\bibitem[Li12]{li12}
Frank Li, Prateek Mittal, Matthew Caesar, Nikita Borisov,
\textit{SybilControl: Practical Sybil Defense with Computational Puzzles},
arXiv:1201.2657, 2012

\bibitem[Sit02]{sit02}
Emil Sit, Robert Morris,
\textit{Security Consideration in Peer-to-Peer Distributed Hash Tables},
Revised Papers from the First International Workshop on Peer-to-Peer Systems,
IPTPS '01, 2002, p. 261--269

\bibitem[Awe10]{awe10}
Baruch Awerbuch, Christian Scheideler,
\textit{Robust Random Number Generation for Peer-to-Peer Systems},
Distributed Computing and Networking vol. 5935, 2010, p.195-206

\bibitem[Wan08]{wan08}
Peng Wang, James Tyra, Eric Chan-Tin, Tyson Malchow, Denis Foo Kune, Nicholas
Hopper, Yongdae Kim,
\textit{Attacking the Kad Network},
Proceedings of the 4th International Conference on Security and Privacy in
Communication Networks, SecureComm '08, article no. 23

\bibitem[May02]{may02}
Petar Maymounkov and David Mazieres,
\textit{Kademlia: A Peer-to-Peer Information System Based on the XOR Metric},
IPTPS '01 Revised Papers from the First International Workshop on Peer-to-Peer
Systems, p. 53-65

\bibitem[Tim11]{tim11}
Juan Pablo Timpanaro, Thibault Cholez, Isabelle Chrisment, Olivier Festor,
\textit{When KAD meets BitTorrent - Building a Stronger P2P Network},
HotP2P 2011, May 2011, Anchorage, ALASKA, United States.

\end{thebibliography}
