\chapter{DHT, its weaknesses, and defense mechanisms}
\label{ch:threats}
\section{Chapter overview}
  In this chapter we define what is a Distributed Hash Table and specify
  Kademlia DHT protocol, describe reasons and methods of attacks on DHT, and
  present examples of different classes of protection mechanisms.
  Finally, we provide examples of effectiveness of described attacks on popular,
  real-world DHT deployments.
  Those examples show that securing DHT is still an open problem in practice.

  This chapter serves also as a survey of related work for Ghoul.
  Since our another contribution is dfuntest, but it touches a different field 
  (testing automation), therefore dfuntest's related work will be presented in
  chapter \ref{ch:dfuntest}.

\section{DHT overview}

  Distributed hash table is a type of a Peer-To-Peer system providing topology
  creation and maintenance protocols.
  They are typically designed for (and tightly coupled) with data storage
  protocols for key-value pairs, hence the hash table part in the name.
  Popular DHT designs include: Chord~\cite{sto03}, Pastry \cite{row01}, Kademlia
  \cite{may02}.

  A structure of a typical DHT consists of a three main components. The first is
  the key space, a collection of identifiers such as 160-bit bitstrings.
  Those keys are an abstract identification of a node and serve to partition the
  key space into ownership ranges over the network.
  The second is an overlay network --- a topology induced by routing tables.
  Routing tables contain pairings between abstract keys and network addresses.
  Neighborhood tables are kept and maintained by each node.
  The third component of DHT specification are protocols for routing table
  maintenance and search of nodes that are not neighbors.

  This kind of structure has certain desirable properties. Firstly, a DHT is
  completely decentralized. Every peer plays the same role and the protocol does
  not require any form of central coordination.
  Secondly, DHTs are scalable.
  In most protocols the size of a routing table is in the order of $O(\log n)$,
  where $n$ is size of the network. Message count complexity of node search
  protocol is logarithmic as well. Thirdly, DHTs are fault tolerant. In fact
  their protocols are designed to be resilient to even significant churn in the
  network. Churn is the rate of nodes' join/leave speed. To counteract that
  phenomena the routing table should be updated often enough.
 
  \subsection{Kademlia}
  Kademlia \cite{may02} is a popular choice among many Peer-to-Peer
  applications. It is well-known for its use in BitTorrent and eDonkey
  file-sharing applications. Wang and Kangasharju \cite{wan13} measure the size
  of Kademlia used in BitTorrent to peak at almost 25 million users.

  A node in Kademlia network is represented by an n-bit binary key (most popular
  choices are $n = 128$ or $n = 160$). Kademlia defines a distance in the
  key space as the xor function. That is distance between two keys $x, y$ is

  \[ d(x, y) = x \oplus y\]

  The routing table is a collection of $n$ buckets, where each bucket has
  maximum size $k$~---~a~\mbox{system-wide} constant. 
  The $i$'th bucket of node with key $x$ holds active and recently seen nodes
  with keys $y$ such that $2^i \leq d(x, y) < 2^{i+1}$.

  Kademlia node implements 4 remote procedure call (RPC) queries. In this
  context RPC is an inter-process communication protocol that defines a query
  message and an algorithm producing a response message for the query. These
  query messages are:

  \begin{description}
    \item{\texttt{FIND\_NODE}} This query is parametrized by a key that the sender
      wants to find. The response should consists of up to $k$ keys closest to
      the searched key in queried node's routing table including the recipient
      node itself.
    \item{\texttt{PING}} This query serves as a heart-beat and node's liveness
      check. It should be answered with a \texttt{PONG} message.
    \item{\texttt{PUT\_KEY}} Orders the recipient to store given (key, value) pair
      in its local storage. This message should be sent to multiple nodes close
      to the pair's key so as to replicate the data.
    \item{\texttt{GET\_KEY}} Structurally the same as the \texttt{FIND\_NODE}
      message. The recipient should return $k$ closest neighbors plus a (key,
      value) pair if it's present in its storage.
  \end{description}

  The main protocol in Kademlia is the node search protocol shown in
  algorithm~\ref{alg:node_search_alg}. Its distinctive feature is that it is
  iterative and performs parallel queries. This form of natural redundancy is
  well suited for preventing some attacks \cite{sit02}.

  \begin{algorithm}
    \begin{algorithmic}[1]
    \STATE \texttt{candidates} $\leftarrow$ empty priority queue for candidate
    nodes ordered by closeness to key $y$
    \STATE Add all nodes from the routing table and the current node to
    \texttt{candidates}
    \STATE Set added nodes' state to \texttt{unqueried}
    \WHILE {$|$nodes whose state isn't \texttt{responded} among top $k$
    candidates$| > 0$}
    \WHILE {$|$nodes with state \texttt{queried} among top $k$
      candidates$| < \alpha$ \AND \\
      $|$nodes with state \texttt{unqueried} among top $k$
            candidates$| > 0$}
        \STATE $n \leftarrow$ first \texttt{unqueried} node in
          \texttt{candidates} 
        \STATE Send \texttt{FIND\_NODE} to $n$
        \STATE $n$'s state $\leftarrow$ \texttt{queried}
    \ENDWHILE
    \COMMENT{maintain up to $\alpha$ parallel queries}
      
    \STATE $e \leftarrow$ response or timeout
    \IF{$e$ is a response}
      \STATE $n \leftarrow$ $e$'s sender
      \STATE $n$'s state $\leftarrow$ \texttt{responded}
      \STATE Add new candidates from response's neighbor list to
      \texttt{candidates}
    \ELSE
      \STATE $n \leftarrow$ timed-out node
      \STATE Remove $n$ from \texttt{candidates}
    \ENDIF
    \ENDWHILE
    \STATE Return first $k$ nodes in \texttt{candidates}.
  \end{algorithmic}
    \caption{Node search protocol for key $y$}
    \label{alg:node_search_alg}
  \end{algorithm}

  The protocol for finding stored data associated with a key is structurally the
  same.
  Only, instead of \texttt{FIND\_NODE}, \texttt{GET\_KEY} is sent and the reply
  additionally contains stored data if any exists.

  Because the distance metric is symmetric, Kademlia does not require
  specialized routing table maintenance messages.
  With every message receipt the recipient node adds the sender to its routing
  table if there is space in the appropriate bucket.
  If there is no space then it sends a \texttt{PING} message to the least
  recently seen node in the given bucket.
  If the intended recipient of the \texttt{PING} message times out then it is
  replaced by the candidate.

\section{Attacks}

  Attacks on a DHT can have three different goals:
  \begin{description}
    \item{\textbf{Denial of service:}} the attacker aims to either stop the
      entire system from functioning or deny access to a part of it.
    \item{\textbf{Spoofing:}} the attacker wants to provide false data to other
      nodes or control them.
    \item{\textbf{Information:}} the attacker wants to gather information about
      participants' activity.
  \end{description}

  DHTs' combination of Peer-to-Peer relationships and structural topology makes
  them vulnerable to attacks which abuse topological dependencies and structural
  constraints to facilitate these attacks. There are two major classes of
  methods which use DHTs' structure to help attackers achieve their goal.

  Firstly, if an attacker controls routing tables of other nodes then it is easy
  to control information flow and therefore the system. An attack which poisons
  routing tables of other nodes by disproportionately filling them with entries
  to colluding malicious nodes is called an \textbf{eclipse attack}.
  The name comes from one of its effects: if a node's routing table is filled
  with malicious nodes the node is effectively partitioned from the rest of the
  network.

  Secondly, DHTs operate on an ephemeral sense of identity represented by a key.
  A \textbf{Sybil attack} happens when an attacker uses a single physical
  computer to represent multiple DHT nodes, therefore increasing his power
  without incurring additional cost \cite{dou02}.
  Since most protocols rely on honest nodes having a majority (especially
  eclipse protection mechanisms), a Sybil attack can shut down the system by
  even a modest attacker.

  We recognize three main vulnerabilities which are responsible for the
  easiness with witch those methods can be used:

  \begin{enumerate}
    \item Node identity is a virtual concept and lacks connection to the real
      world. DHTs as a distributed storage space rely on data, message
      redundancy, and cohesiveness of the topology. Redundancy and cohesiveness
      are easily broken if an attacker may either arbitrarily place itself in
      the topology and fill routing tables with colluding nodes (Eclipse attack)
      or get as many nodes as the attacker wants (Sybil attack).

    \item Each node only maintains a local view over the network, which does not
      provide enough context to detect and prevent some types of malicious
      behavior.
      Malicious behavior is often indistinguishable from honest one unless we
      have knowledge about global state and history.
      Sometimes even that is not enough: for example, randomness of an
      independent node's key is unverifiable without specialized cryptographical
      techniques.

   \item  Key generation is not verifiable. There is no way for a node to verify
     whether given key has been generated randomly.
     It is possible to use a statistical tests to verify uniformity constraints,
     but they are often not enough to accuse specific node of malicious
     behavior.
  \end{enumerate}

\subsection{Other forms of attack}
  Eclipse and Sybil attacks do not constitute the goal of an attack, but are
  used to facilitate it. Such goal are usually to deny access to a resource or
  to fabricate it.

  Attacks that aim to fake possession of requested resource are best countered
  with cryptographic primitives. Using signatures, self-certifying data, or
  Merkle hash trees, like in BitTorrent, is an effective and efficient
  deterrent. To protect against malicious nodes dropping data or routing
  information the system needs to use replication and redundant routing
  \cite{dou02}. 

  Replication against malicious opponents is trickier than without them.
  There are two main strategies for replication: place given resource at nodes
  with key close to the key of the resource; or spread it over the network
  \cite[p.  38]{urd11}.
  The first strategy allows for more efficient retrieval in DHTs such as
  Kademlia or Pastry, but is also more vulnerable to a localized eclipse attack.
  Both strategies are easy to attack if an attacker has ability to choose her
  identifier arbitrarily and therefore a secure DHT requires secure node id
  assignment.

\section{Prevention mechanisms}
\subsection{Eclipse attack prevention mechanisms}

  Sit and Morris \cite{sit02} have been among the first to discuss general
  guidelines against preventing attacks in DHT networks. They advise designing
  the system with verifiable constraints so that a node can distinguish
  malicious behavior from the honest one and provide a proof to other nodes.
  Mechanisms, mainly data and node look up, should have a built-in redundancy so
  that a malicious node presence can be avoided in at least one path of
  execution. The lookup itself should be interactive and allow for clear view of
  progress, which allows a node to verify its correctness and initiate
  redundancy protocols if necessary. Finally, as in any distributed system,
  points of single responsibility should be avoided for obvious reasons.
  
  \subsubsection{Constrained routing table}
  Castro et al. \cite{cas02} have modified Pastry with additional constrained
  routing table and back up routing mechanism to protect against eclipse
  attacks.
  It is difficult for an attacker to inject malicious entries if node key
  assignment is truly random and routing table entries are strictly specified;
  if there exists only one node in the system that may fill given routing table
  entry then key randomness prevents a malicious node from injecting itself into
  that entry without generating large number of keys.
  DHTs such as Kademlia and Pastry are therefore more vulnerable than Chord in
  that regard.

  \subsubsection{Node scrambling}
  A different method to mitigate an eclipse attack is to constantly move node
  ids in unpredictable ways so that it is unfeasible to eclipse a local
  key space. Condie et al. \cite{con06} show that a periodical random,
  unpredictable node reassignment significantly improves Castro's solution.
  This reassignment should be augmented by techniques which mitigate negative
  churn effects. For example: grouping nodes into different timeout groups so
  that timeouts are not synchronized or precalculation of future routing table.

  Awerbach and Scheideler \cite{awe10}, while proposing a robust, distributed
  random number generator, propose a scheme of global node rearrangement on each
  node join event. They show that using a robust cuckoo rule to move $O(\log n)$
  nodes makes the network resilient to join-leave attacks.

  \subsubsection{Topology graph analysis}
  Singh et al. \cite{sin06} observe that if malicious nodes are only a fraction
  of the network then during an Eclipse attack their in-degree in the graph
  induced by the DHT's topology must be higher than average in-degree of honest
  nodes.
  Therefore they propose a protocol which limits in-degree of nodes.
  Each node $x$ maintains an additional backpointer table, which contains nodes
  having $x$ in their routing tables.
  Every node $y$ periodically checks backpointer tables of their neighbors and
  if they are larger than a global constant or does not contain $y$ then it
  removes $x$ from its routing table.

  This scheme requires the backpointer check to be anonymous, therefore the
  scheme uses a common technique of onion routing using anonymizer network to
  achieve that.

  The scheme is effective at limiting eclipse attacks, but it requires the
  global in-degree bound to be tight, especially for large networks. Authors of
  the paper recommend in-degree of no more than 16 for networks larger than
  20000. Such low bound may decrease the performance of the system.

\subsection{Sybil attack prevention mechanisms}
  Preventing a Sybil attack requires a gatekeeper or, more accurately, a
  bouncer.
  A protocol which prevents a single physical node to enter more than once and a
  way to throw out offenders.
  Creating such a protocol in a fully distributed way is difficult.
  It is hard to achieve adequate security if nodes only have access to their
  immediate surroundings.
  Such a limited view lacks necessary information to distinguish between benign
  and malicious behavior.
  Additionally it's much easier to simply eclipse a node. Protocols that
  overcome this obstacle by sharing information globally (\cite{cas02},
  \cite{wan05}) do so at the cost of performance and scalability. Such cost
  may make a DHT unpractical for larger networks. That's why a central authority
  is preferred if it is adequate. This authority serves as a trusted entry point
  to the network. The authority generates signed random keys for newcomers and
  checks global constraints.

  Central authority has well-known drawbacks. Most of them stem from the fact
  that such authority represents a single point of failure.
  A failure of this authority may cause shutdown of the network.
  Compromised authority is a security risk.
  It also acts negatively on scalability of the solution.
  
  Apart from technological disadvantages the central authority is often an
  organizational problem.
  It forces an agent to maintain it in order to provide a service.
  This is done reluctantly since it makes the agent responsible for maintaining
  the service and Peer-to-Peer user community may be distrustful over
  centralized solution.

  The conclusion that only central authority solutions are practical for
  prevention of Sybil attacks was first deduced by \cite{dou02}.
  \cite{dou02} is the first paper studying Sybil class of attacks
  (\cite{urd11}).

  \subsubsection{Centralized gatekeeper}
  Castro et. al. \cite{cas02} agree with \cite{dou02} conclusion and propose
  using a set of central trusted authorities which certify random key and public
  key pair. They suggest adding an IP address to the certificate, so that the
  certificate would be binded to physical host. Unfortunately this solution is
  known to be problematic. Firstly, IP address can be spoofed and with IPv6
  privacy extensions\footnote{IPv6 privacy extensions allow the host to combine
    the assigned network prefix with a random identifier.
    This combination increases the available pool of addresses and makes it more
    difficult to track the device.  \cite{nar01}}
  changed all together, rendering this solution completely
  insecure in the future.
  
  Secondly, using IP for identification causes a problem for users behind NAT or
  with a changing IP address.
  Thirdly, it hinders privacy protection mechanisms.
  Nevertheless using IP address is easy to implement and practical for many
  current DHT networks.

  A centralized gatekeeper gives much flexibility in implementing an
  authentication and Sybil attack prevention scheme. For example there may be
  required a small monetary payment for entry into the DHT network or a
  computational puzzle may have to be solved.

  \subsubsection{Distinction based on a network footprint}

  Without centralized authority network peers would have to register new nodes
  in a distributed way. To distinguish distinct identities from Sybil copies
  they may use network characteristics.
  Such characteristics are usually easy to check (any node may do the check),
  giving low barrier of entry to the network, but it carries an
  assumption that footprints are unfalsifiable, which is not always the case.

  A simple ID calculation based on the IP address and the port number is
  proposed by Dinger and Hartensteing \cite{din06}.
  They propose that a node would register at $r$ Chord registration nodes whose
  position is calculated from hash of node's ID.
  If majority of registration nodes accept the new node then
  it is said to be accepted.
  A node registration fails if the number of nodes with given IP address exceeds
  a constant $a$.
  This solution requires all nodes to confirm validity of their neighbors.

  IP addresses may be spoofed and cause a problem for NAT users.
  Wang~et.~al.~\cite{wan05} proposed adding router's IP and MAC address
  and RTT measurements between the node a designated set of landmarks. A similar
  idea may be found in Bazzi~and~Konjevod~\cite{baz05} where nodes are put
  into $d$-dimensional space based on physical location of a node. Nodes are
  said to be distinct if their coordinates are far away enough.

  \subsubsection{Distinction based on a social network}

  Another class of defenses uses a social network, a graph of trust
  relationships established by humans, to discover or mitigate a Sybil attack
  \cite{urd11}.
  In such defenses it is assumed that each node can verifiably identify itself
  as a node in the social network and that each edge forms a trust relationship
  which means that two people are friends and that they trust each other not to
  launch a Sybil attack. If any node was to launch a Sybil attack then the
  social network graph will exhibit special properties which may be detected. 

  Although such schemes show good performance, both in terms of application
  overhead and attack detectability, they are difficult to apply in real world
  applications. The biggest problem is to generate or acquire a social graph of
  sufficient quality. The core idea in these schemes is that social graph
  represents high-quality human trust relationships. Creation of such a graph
  takes time and motivation. Many users may object to this, because using this
  scheme deprives them of anonymity which for many Peer-to-Peer application
  users is an important factor.

  SybilGuard \cite{hai06} mitigates effects of a Sybil attack by limiting the
  number of Sybil nodes and recognized Sybil groups. It defines the edges
  between honest nodes and Sybil nodes as attack edges and notes that in a
  social graph there can be only few such edges. Then it allows a node to
  partition its neighbors into classes and guarantees with high probability
  that a number of classes that contain a Sybil node is limited by the number of
  attack edges. Although the scheme does not detect Sybil nodes it gives a
  guarantee that with a sufficient redundancy an attacker will not be able to
  intercept a query or manipulate data.

  \subsubsection{Computational puzzles}
  SybilControl\cite{li12} is a distributed scheme for Sybil prevention using
  computational puzzles. Every node is supposed to periodically generate a
  puzzle for itself based on puzzles of its neighbors and solve it. Such puzzle
  is verifiable by any node using novel multi-hop verification and serves as a
  proof-of-work. Nodes that can not present an up-to-date proof-of-work are
  suspected of being a Sybil identity and removed from routing tables. This
  effectively bounds a number of Sybil identities an attacker can create.

  Computation puzzles have the advantage of being flexible. They can be done by
  any node, provided it has enough resources. Challenging hosts can also scale
  puzzles' difficulty. It is also much harder for an attacker to fake
  solving them or use social engineering like in social network solutions.

\section{Examples of real attacks}
These are not just theoretical divagations, but discussed attacks are really
used in practice and are effective.

\paragraph{Hijacking attack}
\cite{wan08} describes an attack on Kad network implementation which was used
in eMule file-sharing application before 2013. This attack is a version of a
routing table poisoning attack in which the attacker abuses lack of
authentication and admission of control which allows any node to advertise as
any other. The attack is split into two phases:
\begin{enumerate}
  \item In the preparation phase the attacker sets up N uniformly distributed
    virtual nodes which gather routing table information of their neighbors.
  \item In the attack phase each attacking node send to its neighbors bogus
    updates of the form \texttt{(ID\_B, IP\_A)}, where \texttt{ID\_B} is the key
    of existing victim node present in the recipient's routing table and
    \texttt{IP\_A} is the attacker's IP address.
\end{enumerate}

Authors show that with just 100Mbps bandwidth they were able to successfully
deny 80\% of keyword queries after 1-hour long preparation phase with a
network with 16000 nodes.
Unfortunately for the attacker, this cost is ongoing since the attacking node
needs to be responsive.

Authors also provide a version of this attack where, instead of providing
attacker's IP, the IP of the attacked node is used. eMule at the time did not
provide any check against this behavior so it would be effective in blocking
any effective look up. They also calculate that in this version it would take
around 200Mbps of network speed to attack the entire 1 million eMule network
with the result of blocking up to 75\% queries.

More recent versions of eMule contain basic protections against attacks
\cite{tim11}, such as:
\begin{description}
  \item{\textbf{Flood protection}} The number of messages received from one IP
    in a given time-frame is limited.
  \item{\textbf{IP limitations}} Only one node with given IP can be present in
    the routing table.
  \item{\textbf{IP verification}} Before a contact is added a three-way
    handshake is performed.
\end{description}

While those protections defend against small and unsophisticated attack it must
be noted that the Kad network is still vulnerable to moderately determined and
resourceful attacker.

\paragraph{Feasibility of Sybil attack}
Although Sybil attack is more expensive than above mentioned Hijacking attack
\cite{tim11} has shown that in Mainline DHT, implementation of Kademlia used in
BitTorrent, it is still easy. In their experiment they were able to fill
neighbors routing table with 160 Sybil nodes within 5 minutes after the attack
phase has begun. While similar attack would be impossible in newer versions of
Kad the only limitation is the fact that only one IP address is used.

\paragraph{Measurements of present attacks}
It is very easy to launch a Sybil attack in Mainline DHT and such attacks have
distinctive footprint. Wang \cite{wan12a} has set up honeypots in the Mainline
DHT to detect and analyze possible Sybil attackers. He discovered an attacker
using a hijacking method described earlier running on Amazon's cloud who
maintains over 300.000 Sybil nodes. This attacker didn't seem to do much
and might have been just monitoring the network. A different attacker was
impersonating specific key space ranges and had a distinctive IP address
belonging to an international ISP service.
The attacker was redirecting queries from inside its domain
to other nodes inside it, localizing the traffic.

Authors conclude that although those attacks didn't seem to do much global harm,
the easiness with which they are executed proves that there are no costly
barriers to launching a successful attack to disable majority of DHT queries.
